$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-06 paper/paper.tex
For uniformity, always mention textsc-d type name in definition titles

\begin{nidefinition}[Types and typing contexts]
  A \emph{type} is either a unit type ($\unit$), a base type ($\base{n}$) or a channel type ($\channel{t}{x}$) (\autoref{fig:prectx}).

@@

\begin{nidefinition}[Usage contexts]
  A \emph{usage context} is a context $\Ctx_{idxs}$ of usage annotations that is indexed by a length-indexed context of indices $\Idxs_n$ (\autoref{fig:ctx}).

>>>>

\begin{nidefinition}[\textsc{Type} and \textsc{PreCtx}: types and typing contexts]
  A \emph{type} is either a unit type ($\unit$), a base type ($\base{n}$) or a channel type ($\channel{t}{x}$) (\autoref{fig:prectx}).

@@

\begin{nidefinition}[\textsc{Ctx}: usage contexts]
  A \emph{usage context} is a context $\Ctx_{idxs}$ of usage annotations that is indexed by a length-indexed context of indices $\Idxs_n$ (\autoref{fig:ctx}).
